Spectral Variability of Two Rapidly Rotating Brown Dwarfs: \\2MASS~J08354256$-$0819237 and 2MASS~J18212815+1414010

### 2017-02-26 ms.tex
I updated the temperature spot model drawing and curves.

\begin{figure*}
\centering
\subfloat[2MASS J0835]{
	\includegraphics[width=0.5\textwidth]{amp_vs_wavl_j0835.pdf}
	\label{fig:ampspec0835}
	}
\subfloat[2MASS J1821]{
	\includegraphics[width=0.5\textwidth]{amp_vs_wavl_j1821.pdf}
	\label{fig:ampspec1821}
	}
	\caption{Sine fit amplitude versus wavelength for each brown dwarf. \sha\ shows no clear trend in wavelength, while \shb\ has a strong slope indicative of Mie-scattering particles.
	 Also shown in the figure for \shb\ is the WFC3 amplitude from \citet{2015ApJ...798L..13Y}. The WFC3 observations were from a different epoch, with different cloud coverage, but show a similar slope.
	 The amplitude spectrum for \shb\ is fit with a simple Mie scattering models for a log-normal particle size distribution of spherical forsterite grains with a best-fit radius of 0.17 $\pm$ 0.01 grains.}
	\label{fig:ampSpec}
\end{figure*}

@@

Each of the light curves were fit to a simple sinusoidal model:
\begin{equation}\label{eq:cosfit}
F(t) = A \cos(2 \pi (t - t_t)/\tau) + B t + C
\end{equation}
where $F(t)$ is the relative flux as a function of time $t$, $A$ is the amplitude of periodic variations, $t_t$ is the time of maximum periodic flux, $\tau$ is period of the variations, and $B$ and $C$ are linear terms describing any baseline trend.
Since some wavelengths are affected by telluric contamination and we wish to avoid fitting harmonics, we impose a prior on the rotational period $\tau$.
For \sha\ we use a prior 3.0 $< \tau < $3.2 hr from \citet{2004MNRAS.354..378K} and for \shb\ we use 3.8 $< \tau <$ 4.0 hr.
The prior for \shb\ is slightly different from the value from \citet{2015ApJ...799..154M}(4.2 hr) because it came from a fit in a clear region of the time series (at 1.08~$\mu$m) where a double sinusoidal fit resulted in a period of 3.90 $\pm$ 0.01 hr.
Secondly, we restrict the time of maximum periodic flux such that $-\tau/2 < t_1 < \tau/2$ to make sure there are no 2$\pi$ degeneracies in the fit.

@@

The same trend of decreasing variability amplitude for \shb\ was observed by HST's WFC3 grism over a shorter wavelength range (1.1 to 1.7~$\mu$m) by \citet{2015ApJ...798L..13Y}, also shown in Figure \ref{fig:ampspec1821}.
The HST WFC3 maximum over minimum flux spectrum is converted to an amplitude spectrum by assuming that the amplitude is half the difference in maximum and minimum flux, which can be shown to be 
\begin{equation}
A  = \frac{f_R - 1}{f_R + 1}
\end{equation}\label{eq:ampFromRatio}
where $f_R$ is the flux ratio of the maximum over minimum flux.
There is a multiplicative offset between the IRTF and WFC3 spectrum because they were taken at different epochs and therefore different spatial cloud and temperature distributions.
\citet{2015ApJ...798L..13Y} find that the WFC3 spectrum has no significant water vapor absorption which indicates a high haze layer in 2MASS J1821 and is consistent with our gradually decreasing slope from 1.1 to 1.7~$\mu$m.

@@

Another simple model we attempt assumes  that the brown dwarf spectral variability has to do with a non-uniform temperature distribution on the brown dwarf in the same way that starspots modulate the brightness of hydrogen burning stars as they spin.
In Figure \ref{fig:ampspec1821tdiff}, we fit the same amplitude spectrum as in Figure \ref{fig:ampspec1821}.
This time we model the data with two temperature regions as shown in Figure \ref{fig:tdiffschem}, with two opposite longitudes of the planet at the brightness minimum and maximum.
We assume for the purposes of variability that each hemisphere and layer is in local thermodynamic equilibrium (LTE) so that the flux is proportional to the Planck function times the areal coverage.
The flux ratio between maximum and minimum flux is then
\begin{equation}
f_{R,\lambda} = \frac{\alpha_1 B_\lambda(T_1) + (1-\alpha_1) B_\lambda(T_2)}{\alpha_2 B_\lambda(T_1) + (1-\alpha_2) B_\lambda(T_2)}
\end{equation}
where $\alpha_1$ and $\alpha_2$ are the areal fractions of the first ($T_1$ and second ($T_2$) regions respectively, $B_\lambda$ is the Planck function, and $T_1$ and $T_2$ are the temperatures of the two regions.
$\alpha_1$ and $\alpha_2$ are limited to [0,1].
Using equation \ref{eq:ampFromRatio}, the amplitude then becomes
\begin{equation}\label{eq:twoTempAmpAlphas}
A_\lambda = \frac{\left(\alpha_1 - \alpha_2 \right) \left(B_\lambda(T_1) - B_\lambda(T_2) \right)}{\left(\alpha_1 + \alpha_2\right) B_\lambda(T_1) + \left(2 - \alpha_1 - \alpha_2\right) B_\lambda(T_2)}.
\end{equation}
If the temperature difference is significant so that one Planck function is in the Wien's limit while the other is in the Rayleigh Jeans tail, the cooler temperature essentially becomes black and the contrast approaches a constant for short wavelengths.
If we ignore projection effects for small area coverage, the effective temperature is 
\begin{equation}
\sigma T_{eff}^4 \approx (\alpha_1 + \alpha_2) \sigma T_1^4 + (2 - \alpha_1 - \alpha_2) \sigma T_2^4
\end{equation}
where $\sigma$ is the Stephan-Boltzmann constant.

@@

We start by considering a two-faced model where $\alpha_1$ = 1 and $\alpha_2$ = 0, so that the two halves of the brown dwarf are different temperatures.
To be close to the effective temperature of the brown dwarf, we fix $T_1$ to be 1600 K and only vary $T_2$.
This model is a poor match to the data, also shown in Figure \ref{fig:ampspec1821tdiff} with a reduced chi-squared, $\bar{\chi}^2$ = 15.
Next, we attempt a model where we allow $\alpha_1$ and $\alpha_2$ to be free parameters and restrict the temperature limits of the two regions to [1300,2500] to ensure that the final effective temperature is close to the measured 1600 K \citep{gagne2015banyan7}.
The best fit model has $T_{eff} \approx $1590 K and $\bar{\chi}^2$=2.1, but pushes to the edges of our prior with $T_1$ = 2500 K and $T_2$ = 1300 K.
Finally, we consider a model where all four parameters, $\alpha_1$, $\alpha_2$, $T_1$ and $T_2$ are all free.
With these loose constraints, the model fits the data with $\bar{\chi}^2$ = 1.3, consistent with the data, but not with the effective temperature ($T_{eff}$ = 850 K).
The $\alpha$ values are both $<<1$, indicating that the model fits with dark patches on a small fraction of the surface. [I MODIFIED THIS SENTENCE; IS IT CORRECT? I'm a little confused about how both $\alpha$ values can be $<<1$; if one is small doesn't the other have to be large?]

@@

2MASS J1821 shows significant variability up to the 1.1\% amplitude at short wavelengths (0.8$\mu$m) which decreases towards the near infrared (2.4$\mu$m).
This is consistent with HST measurements for the system that show a gradual decrease in variability amplitude with wavelength \citep{2016ApJ...826....8Y} from 1.1$\mu$m to 1.7 $\mu$m with no decrease in the water vapor band.
The lack of the water vapor band gives evidence of a high altitude aerosol layer in the atmosphere.

>>>>

\begin{figure*}
\centering
\subfloat[2MASS J0835]{
	\includegraphics[width=0.5\textwidth]{amp_vs_wavl_j0835.pdf}
	\label{fig:ampspec0835}
	}
\subfloat[2MASS J1821]{
	\includegraphics[width=0.5\textwidth]{amp_vs_wavl_j1821.pdf}
	\label{fig:ampspec1821}
	}
	\caption{Sine fit amplitude versus wavelength for each brown dwarf. \sha\ shows no clear trend in wavelength, while \shb\ has a strong slope indicative of Mie-scattering particles.
	 Also shown in the figure for \shb\ is the WFC3 amplitude from \citet{2015ApJ...798L..13Y}. The WFC3 observations were from a different epoch, with different cloud coverage, but show a similar slope.
	 The amplitude spectrum for \shb\ is fit with a simple Mie scattering models for a log-normal particle size distribution of spherical forsterite grains with a best-fit radius of 0.17 grains.}
	\label{fig:ampSpec}
\end{figure*}

@@

Each of the light curves were fit to a simple sinusoidal model:
\begin{equation}\label{eq:cosfit}
F(t) = A \cos(2 \pi (t - t_t)/\tau) + B t + C
\end{equation}
where $F(t)$ is the relative flux as a function of time $t$, $A$ is the amplitude of periodic variations\footnote{The total amplitude is 2$A$ in our convention.
Some other conventions describe $A$ as a ``semi-amplitude''}, $t_t$ is the time of maximum periodic flux, $\tau$ is period of the variations, and $B$ and $C$ are linear terms describing any baseline trend.
Since some wavelengths are affected by telluric contamination and we wish to avoid fitting harmonics, we impose a prior on the rotational period $\tau$.
For \sha\ we use a prior 3.0 $< \tau < $3.2 hr from \citet{2004MNRAS.354..378K} and for \shb\ we use 3.8 $< \tau <$ 4.0 hr.
The prior for \shb\ is slightly different from the value from \citet{2015ApJ...799..154M}(4.2 hr) because it came from a fit in a clear region of the time series (at 1.08~$\mu$m) where a double sinusoidal fit resulted in a period of 3.90 $\pm$ 0.01 hr.
Secondly, we restrict the time of maximum periodic flux such that $-\tau/2 < t_1 < \tau/2$ to make sure there are no 2$\pi$ degeneracies in the fit.

@@

The same trend of decreasing variability amplitude for \shb\ was observed by HST's WFC3 grism over a shorter wavelength range (1.1 to 1.7~$\mu$m) by \citet{2015ApJ...798L..13Y}, also shown in Figure \ref{fig:ampspec1821}.
The HST WFC3 maximum over minimum flux spectrum is converted to an amplitude spectrum by assuming that the amplitude is half the difference in maximum and minimum flux, which can be shown to be 
\begin{equation}\label{eq:ampFromRatio}
A  = \frac{f_R - 1}{f_R + 1}
\end{equation}
where $f_R$ is the flux ratio of the maximum over minimum flux.
There is a multiplicative offset between the IRTF and WFC3 spectrum because they were taken at different epochs and therefore different spatial cloud and temperature distributions.
\citet{2015ApJ...798L..13Y} find that the WFC3 spectrum has no significant water vapor absorption which indicates a high haze layer in 2MASS J1821 and is consistent with our gradually decreasing slope from 1.1 to 1.7~$\mu$m.

@@

Another simple model we attempt assumes  that the brown dwarf spectral variability has to do with a non-uniform temperature distribution on the brown dwarf in the same way that starspots modulate the brightness of hydrogen burning stars as they spin.
In Figure \ref{fig:ampspec1821tdiff}, we fit the same amplitude spectrum as in Figure \ref{fig:ampspec1821}.
This time we model the data with two temperature regions as shown in Figure \ref{fig:tdiffschem}, with two opposite longitudes of the planet at the brightness minimum and maximum.
We assume for the purposes of variability that each hemisphere and layer is in local thermodynamic equilibrium (LTE) so that the flux is proportional to the Planck function times the areal coverage.
The flux ratio between maximum and minimum flux is then
\begin{equation}
f_{R,\lambda} = \frac{\alpha_1 B_\lambda(T_1) + (1-\alpha_1) B_\lambda(T_2)}{\alpha_2 B_\lambda(T_1) + (1-\alpha_2) B_\lambda(T_2)}
\end{equation}
where $\alpha_1$ and $\alpha_2$ are the areal fractions of the first temperature ($T_1$) for the first and second hemispheres respectively, $B_\lambda$ is the Planck function, and $T_1$ and $T_2$ are the temperatures of the two regions.
$\alpha_1$ and $\alpha_2$ are limited to [0,1].
Using equation \ref{eq:ampFromRatio}, the amplitude then becomes
\begin{equation}\label{eq:twoTempAmpAlphas}
A_\lambda = \frac{\left(\alpha_1 - \alpha_2 \right) \left(B_\lambda(T_1) - B_\lambda(T_2) \right)}{\left(\alpha_1 + \alpha_2\right) B_\lambda(T_1) + \left(2 - \alpha_1 - \alpha_2\right) B_\lambda(T_2)}.
\end{equation}
If the temperature difference is significant so that one Planck function is in the Wien's limit while the other is in the Rayleigh Jeans tail, the cooler temperature essentially becomes black and the contrast approaches a constant for short wavelengths.
If we ignore projection effects for small area coverage, the effective temperature is 
\begin{equation}
\sigma T_{eff}^4 \approx (\alpha_1 + \alpha_2) \sigma T_1^4 + (2 - \alpha_1 - \alpha_2) \sigma T_2^4
\end{equation}
where $\sigma$ is the Stephan-Boltzmann constant.

@@

We start by considering a two-faced model where $\alpha_1$ = 1 and $\alpha_2$ = 0, so that the two halves of the brown dwarf are different temperatures.
To be close to the effective temperature of the brown dwarf, we fix $T_1$ to be 1600 K and only vary $T_2$.
This model is a poor match to the data, also shown in Figure \ref{fig:ampspec1821tdiff} with a reduced chi-squared, $\bar{\chi}^2$ = 15.
Next, we attempt a model where we allow $\alpha_1$ and $\alpha_2$ to be free parameters and restrict the temperature limits of the two regions to [1300,2500] to ensure that the final effective temperature is close to the measured 1600 K \citep{gagne2015banyan7}.
The best fit model has $T_{eff} \approx $1590 K and $\bar{\chi}^2$=2.1, but pushes to the edges of our prior with $T_1$ = 2500 K and $T_2$ = 1300 K.
Finally, we consider a model where all four parameters, $\alpha_1$, $\alpha_2$, $T_1$ and $T_2$ are all free.
With these loose constraints, the model fits the data with $\bar{\chi}^2$ = 1.3, consistent with the data, but not with the effective temperature ($T_{eff}$ = 850 K).
The $\alpha$ values are both $<<1$, indicating that the model fits with bright patches on a small fraction of the surface.
The maximum to minimum contrast in this spot model is sensitive to the relative areas of these bright patches so a small difference in areas controls the maximum over minimum flux.

@@

2MASS J1821 shows significant variability up to the 1.3\% amplitude (2.6\% peak-to-valley) at short wavelengths (0.9$\mu$m) which decreases towards the near infrared (2.4$\mu$m).
This is consistent with HST measurements for the system that show a gradual decrease in variability amplitude with wavelength \citep{2016ApJ...826....8Y} from 1.1$\mu$m to 1.7 $\mu$m with no decrease in the water vapor band.
The lack of the water vapor band gives evidence of a high altitude aerosol layer in the atmosphere.
